Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-19 paper/main.tex
Changes in Section3

%Explain prediction and quantization steps here itself ! (succintly)
\section{Reservoir model for Predictive Quantization}
\label{section3}
\subsection{Vectorizing matrices in Stiefel Manifold}
\label{vectorize}
The reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$.
For brevity, let us assume that such a matrix $\mathcal{\bM}$ is a \'semi-unitary\' matrix.
A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector.
For the third column, we take only the first $N_T-2$ complex numbers, and so on.
Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
For any semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ the vectorized representation.

Observe here that there is a dimensional penalty; upon vectorizing the semi-unitary $\mathcal{\bM}$,
$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold.
We vectorize $\mathcal{\bM}$ to a $2N_TN_R-N_R^2+N_R$ dimensional vector, corresponding to an overhead of $N_R$ dimensions, since we have not exploited the fact that each column vector is a unit norm vector as well.
One could attempt to use only $N_T-1$ complex numbers when vectorizing the first column, rather than all $N_T$.
However, this would lead to a non-unique representation, since there could then be infinitely many values for the missing complex number, all of which yield a unit norm vector.
%Focus on the fact that you don't actually pay a penalty
%The thing to quantize remains on the Stiefel Manifold
\subsection{Forward Prediction $f_P$ function}
\noindent The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
Consider the reservoir computing framework shown in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic

The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, which is the vectorized representation of $\tilde{\bU}_{i,t-1}$.
Let $D_{\text{in}}=2N_TN_R-N_R^2+N_R$ be the dimension of the input vector to the dimension.
Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
\begin{equation}
\br_{i,t}=\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})
\label{res_upd}
\end{equation}
where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics and correlates reservoir state across time, and $\text{tanh}$ is applied element wise.
Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.

The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$.
Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$\footnote{Why it is $t-1$ and not $t$ would surface up in Section \ref{train}}, viz.
\begin{equation}
\bp_{i,t}=\bW^{\text{out}}_{i,t-1}\br_{i,t}
\label{pred_op}
\end{equation}
\begin{figure*}[ht]
\centering
\includegraphics[width=0.8\textwidth]{images/system.pdf}
\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
\label{res_overview}
\end{figure*}
This completes the forward prediction algorithm to obtain $\bP_{i,t}$ using just one past observed $\bU_{i,t-1}$. That is,
\begin{equation}
\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For brevity, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
\label{fwd_pred}
\end{equation}
However, a complete discussion of the prediction algorithm also involves a backward pass, involving the updation of output couplers $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
\subsection{Quantization function $q_P$}
Before proceeding, it is critical to describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
In this work, the chosen lifting-retraction operations are the Cayley Exponentials, elaborated in \cite{DBLP:journals/corr/abs-1708-00045}. % and used in \cite{Gupt1905:Predictive}.
The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.

The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
This codebook is also referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
The feedback from the receiver indicates the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
With the optimum direction chosen, the next step is to determine how much to move in that particular direction, viz. the length of the chosen tangent direction.
For this, we adopt the strategy in \cite{6891198}, which
controls the magnitude of tangent steps, by having two codebooks
$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors from $\text{base}^{\mathcal{C}}$, i.e. $T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook $T^\mathcal{C}$.
The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}. The receiver then feeds back $\text{fb}_{i,t}$ to the transmitter using $\mathcal{B}$ bits. The transmitter uses the fed back $\text{fb}_{i,t}$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
\begin{equation}
\label{eqn:cn1}
\text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
\end{equation}
\begin{equation}
\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
\label{eqn:cn2}
\end{equation}

@@

\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2

@@

\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)

@@

Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,

@@

To conclude this section, we will now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
To support the above statement, observe \eqref{res_upd},\eqref{fpqp} to obtain $\bW^{\text{out}}_{i,t}$ from $\tilde{\bu}_{i,t}$, and \eqref{fwd_pred} to obtain $\bP_{i,t+1}$ combinedly,
\begin{equation*}
\highlight{\bW_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
\end{equation*}
\begin{equation*}
\highlight{\bP_{i,t+1}}=f_P(\tilde{\bU}_{i,t})=\highlight{\bW^{\text{out}}_{i,t}}\text{tanh}(\bA_i\br_{i,t}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t}})
\end{equation*}
The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `'learns' the correlations brought about by $q_P$, in addition to temporal correlations. %Better framing possible
This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.

The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$.
This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
Reservoir computing, thus proposes an easier to implement data centric scheme, which is a rarity for typical data centric ML based schemes.

@@

From Fig. \ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal based predictive quantizer in \cite{6891198}. In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_t$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.

>>>>

%Explain prediction and quantization steps here itself ! (succintly)
\section{Reservoir model for Predictive Quantization}
\label{section3}
\subsection{Vectorizing matrices in Stiefel Manifold}
\label{vectorize}
The traditional reservoir computing framework has inputs and outputs as vectors, and thus, it is necessary to convert the precoder matrices to vectors.
A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $N_T\times N_R$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$.
For brevity, we call such a matrix $\mathcal{\bM}$ to be a `semi-unitary' matrix.
A na{\"i}ve method to vectorize a $N_T\times N_R$ semi-unitary matrix would be to take all it's $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\mathbb{I}_{N_R}$ property, which implies that each vector representing the columns of $\mathcal{\bM}$ is orthogonal to other columns.
For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
For the second column, we take only the first $N_T-1$ complex numbers, since the last number can be determined by utilizing orthogonality with the first vector.
For the third column, we take only the first $N_T-2$ complex numbers, and so on.
Therefore, we can vectorize the $N_T\times N_R$ $\mathcal{\bM}$ into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-(N_R^2-N_R)$ dimensional vector.
For a semi-unitary matrix $\mathcal{\bM}$, denote by $\mathcal{\bm}$ it's vectorized representation.

Observe here that we incur a dimensional penalty upon vectorizing semi-unitary $\mathcal{\bM}$.
$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas $\mathcal{\bm}$ is a $2N_TN_R-N_R^2+N_R$ dimensional vector. This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
It looks as if we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$, but this would lead to a non-unique representation, since there could then be infinite possibilities of the missing one complex number, such that the vector has a norm 1.
%Focus on the fact that you don't actually pay a penalty
%The thing to quantize remains on the Stiefel Manifold
\subsection{Forward Prediction $f_P$ function}
\noindent The vector representation of semi-unitary matrices allows us to proceed with the discussion on reservoir computing framework for predictive quantization of SVD precoders.
Consider the reservoir computing framework shown in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic

The input to the reservoir $i$ corresponding to subcarrier $i$ is $\tilde{\bu}_{i,t-1}$, (the vectorized representation of $\tilde{\bU}_{i,t-1}$) with dimensions $D_{\text{in}}=2N_TN_R-N_R^2+N_R$.
Using a randomly initialized $D_{\text{in}}\times D_{\text{resv}}$ input coupler matrix, $\bW^{\text{in}}_i$, the $D_{\text{in}}$ dimensional input is mapped to a $D_{\text{resv}}$ dimensional vector, where $D_{\text{resv}}$ is the dimension of the reservoir state vector $\br_{i,t}$.
The reservoir state vector $\br_{i,t}$ is initialized with $D_{\text{resv}}$ zeros, and is updated via the following equation,
\begin{equation}
\br_{i,t}=\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})
\label{res_upd}
\end{equation}
where $\bA_i$ is the adjacency matrix that captures the reservoir dynamics, and $\text{tanh}$ is applied element wise.
Typical choices for $\bA_i$ have been Erdos-Renyi graphs with an upper bounded maximum eigen value \cite{mosleh2017brain,pathak2017using}.

The output of the reservoir is $\bp_{i,t}$, a vectorized representation of $\bP_{i,t}$.
Therefore, the output of the reservoir is also a $D_{\text{in}}$ dimensional vector ($D_{\text{out}}=D_{\text{in}}$).
The output $\bp_{i,t}$ is obtained via matrix transformation of the reservoir state $\br_{i,t}$ via the $D_{\text{resv}}\times D_{\text{out}}$ output coupler matrix $\bW^{\text{out}}_{i,t-1}$\footnote{Why it is $t-1$ and not $t$ would surface up in Section \ref{train}}, viz.
\begin{equation}
\bp_{i,t}=\bW^{\text{out}}_{i,t-1}\br_{i,t}
\label{pred_op}
\end{equation}
\begin{figure*}[ht]
\centering
\includegraphics[width=0.8\textwidth]{images/system.pdf}
\caption{An overview of the reservoir computing framework proposed for predictive quantization of $\bu_{i,t}$}
\label{res_overview}
\end{figure*}
This completes the forward prediction to obtain $\bP_{i,t}$ using only the past observed $\bU_{i,t-1}$ (i.e. $p=1$, Section \ref{section2}). That is,
\begin{equation}
\bP_{i,t}=f_P(\tilde{\bU}_{i,t-1})=\bW^{\text{out}}_{i,t-1}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\tilde{\bu}_{i,t-1})\footnote{For brevity, $\bp_{i,t}$ and $\bP_{i,t}$ are treated to be one and the same}
\label{fwd_pred}
\end{equation}
However, a complete discussion of the prediction algorithm also involves a backward pass, involving the updation of output couplers $\bW^{\text{out}}_{i,t}$, which would follow subsequently.
\subsection{Quantization function $q_P$}
Before proceeding, it is critical to describe the quantization function $q_P(\bP_{i,t},\text{fb}_{i,t})$, which is similar to the one used in \cite{6891198,Gupt1905:Predictive,6545375}.
Central to the quantization algorithm is the fact that tangent spaces local to a point in manifold are linear vector spaces.
Given two points $\bX$ and $\bY$ in $\text{St}(N_T,N_R)$, a lifting operation $\bT^Y_X=\texttt{lift}(\bX,\bY)$, $\texttt{lift}:\text{St}(N_T,N_R)\times \text{St}(N_T,N_R) \to \mathcal{T}_X \text{St}(N_T,N_R)$ yields a tangent from $X$ to $Y$, denoted as $\bT^Y_X \in \mathcal{T}_X \text{St}(N_T,N_R)$, where $\mathcal{T}_X \text{St}(N_T,N_R)$ is the local tangent space at $\bX$.
A corresponding retraction operation $Y=\texttt{retract}(X,\bT^Y_X)$, $\texttt{retract}: \text{St}(N_T,N_R)\times \mathcal{T}_X \text{St}(N_T,N_R) \to \text{St}(N_T,N_R)$ gives back the manifold point obtained by traversing in the tangent direction given by the second argument.
In this work, the chosen lifting-retraction operations are the Cayley Exponentials, discussed in \cite{DBLP:journals/corr/abs-1708-00045,Gupt1905:Predictive}. % and used in \cite{Gupt1905:Predictive}.
The Cayley exponential lifting operation maps two points in $\text{St}(N_T,N_R)$, to a $N_T\times N_T$ skew Hermitian matrix that represents the tangent from first point to the other.

The quantization algorithm exploits the linear vector space property of the tangent space and quantizes the local tangent space at the predicted precoder $\bP_{i,t}$, viz $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
The codebook for $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$ corresponds to a collection of codewords that represent the different directions (tangents) in $\mathcal{T}_{\bP_{i,t}} \text{St}(N_T,N_R)$.
This codebook is also referred to as the base codebook ($\text{base}^{\mathcal{C}}$) for the quantization function.
The feedback from the receiver indicates the optimum tangent in the $\text{base}^{\mathcal{C}}$, which the transmitter can choose to get closest (in terms of chordal distance metric, $d_s(\bX,\bY)$ for $\bX,\bY \in \text{St}(N_T,N_R)$ detailed in \cite{Gupt1905:Predictive,6891198}) to the actual value $\bU_{i,t}$.
With the optimum direction chosen, the next step is to determine how much to move in that particular chosen direction, viz. the length of the chosen tangent direction.
For this, we adopt the strategy in \cite{6891198}, which
controls the magnitude of tangent steps, by having two codebooks
$T^{\mathcal{C}}_p,T^{\mathcal{C}}_m$ of different spreads $s_p,s_m$, but same $2^{\mathcal{B}-1}$ base vectors in the $\text{base}^{\mathcal{C}}$, i.e. $T^{\mathcal{C}}_{\{p/m\}}=s_{\{p/m\}}\text{base}^{\mathcal{C}}$ (All codewords $\in \text{base}^{\mathcal{C}}$ multiplied by $s_{\{p/m\}}$ individually).
The two codebooks are concatenated to form a $2^\mathcal{B}$ length codebook $T^\mathcal{C}$.
The receiver finds the optimal index $\text{fb}_{i,t} \in \{1,2,\ldots,2^{\mathcal{B}}\}$ in $T^\mathcal{C}$ by comparing the chordal distance metric ($d_s$), of each codeword to the actual precoder $\bU_{i,t}$ obtained from the SVD of the channel matrix, using \eqref{eqn:cn1}. The receiver then feeds back $\text{fb}_{i,t}$ to the transmitter using $\mathcal{B}$ bits. The transmitter uses the fed back $\text{fb}_{i,t}$ and \eqref{eqn:cn2} to calculate $\tilde{\bU}_{i,t}$,
\begin{equation}
\label{eqn:cn1}
\text{fb}_{i,t} \gets \text{argmin}_{i \in \{1,2,\ldots,2^{\mathcal{B}}\}}\left (d_s\left (\bU_{i,t},\text{retract}(\bP_{i,t},T^\mathcal{C}[i])\right ) \right)
\end{equation}
\begin{equation}
\tilde{\bU}_{i,t}=q_P(\bP_{i,t},\text{fb}_{i,t})=\text{retract}(\bP_{i,t},T^\mathcal{C}[\text{fb}_{i,t}])
\label{eqn:cn2}
\end{equation}

@@

\mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2

@@

\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_{i,t}=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)

@@

Computing the gradients $\frac{\partial \mathcal{O}_{i,t}}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,

@@

To conclude this section, we will now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
The first key advantage of the proposed framework, over the past work \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
To support the above statement, observe \eqref{update_Wt1} to obtain $\bW^{\text{out}}_{i,t-1}$ from $\tilde{\bU}_{i,t-1}=q_P(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1})$, and \eqref{pred} to obtain $\bP_{i,t+1}$,
\begin{equation}
\highlight{\bW_{i,t-1}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-2}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bU}_{i,t-2}),\text{fb}_{i,t-1}),\br_{i,t-1})}{\frac{\text{den}_{i,t-2}}{\lambda}+||\br_{i,t-1}||^2}
\label{update_Wt1}
\end{equation}
\begin{equation}
\highlight{\bP_{i,t}}=f_P(\tilde{\bU}_{i,t-1})=\highlight{\bW^{\text{out}}_{i,t-1}}\text{tanh}(\bA_i\br_{i,t-1}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t-1}})
\label{pred}
\end{equation}
The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `learns' the correlations brought about by $q_P$, in addition to temporal correlations. %Better framing possible
This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_{i,t}$).
The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_{i,t}$.

The second key advantage of the proposed scheme comes from the ease of training the reservoir, entailed by \eqref{res_upd}.
By storing just one matrix $\text{num}_{i,t}$ and a number $\text{den}_{i,t}$, we can capture the enitre history of the precoding matrices, with past values weighted by $\lambda$.
This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $n$ (which has to be pre-decided) precoders in a $n$ sized cyclic buffer kind-of arrangement.
Reservoir computing, thus proposes an easier to train (data centric) scheme, which is a rarity for typical data centric ML based schemes.

@@

From Fig. \ref{qtiz_err} it is evident that the reservoir computing based predictive quantizer is able to reduce the quantization error below what was obtained from the existing temporal based predictive quantizer in \cite{6891198}. In addition, the quantization error is much more smoother, which can be explained from the fact that the reservoir computing approach optimizes, $\mathcal{O}_{i,t}$ which captures the long term dynamics of the channel and hence, is able to correct for jittery variations.
